---
title: "R Notebook"
output: html_notebook
---

# Load data / packages 

```{r}
library(lme4)
library(lmerTest)
library(multcomp)
require(ggplot2)
require(ggiraph)
require(ggiraphExtra)
require(plyr)
library(car)
library(dplyr)
library(tidyverse)
library(broom)
library(multcomp)
library(xtable)
library(broom.mixed)

#install.packages("broom.mixed")
```

##### EXPERIMENT 1 ##### 

# Transmission Fidelity
# Main paper, section 2.2.1
# Biniomial-Logistic regression on number of successes on post-trial questionnaire.
```{r}
learner_concept_knowledge_df <- read.csv("~/src/naive_curriculum_exp/ipython/exp1_df.csv")

# Final level only
learner_concept_knowledge_df <- learner_concept_knowledge_df %>% filter(level_number == 10)

# Sum code communication
learner_concept_knowledge_df$communication <- factor(learner_concept_knowledge_df$communication)
contrasts(learner_concept_knowledge_df$communication) = contr.sum(2)
contrasts(learner_concept_knowledge_df$communication)

# Center complexity
learner_concept_knowledge_df$boolean_complexity_centered <- learner_concept_knowledge_df$boolean_complexity - (1 + 4 + 6)/3

# Multiply percent-of-concept by 8 to get number correct
learner_concept_knowledge_df$successes <- learner_concept_knowledge_df$learner_concept * 8

# Main effects only
xmdl_main = glm(cbind(successes, 8 - successes) ~ communication + boolean_complexity_centered,
            data=learner_concept_knowledge_df, family='binomial')

# Main effects + interaction
xmdl_full <- update(xmdl_main, ~ . + boolean_complexity_centered:communication)
summary(xmdl_full)

anova_comp <- anova(xmdl_main, xmdl_full, test='Chisq')
anova_comp

# Generate table for appendix
# xtable(tidy(xmdl_full))
```

# Inferred Complexity
# Main paper, section 2.2.2 
# Linear model predicting the learner's hypothesized concept complexity.
```{r}
inferred_complexity_df <- read.csv("~/src/naive_curriculum_exp/ipython/exp1_df.csv")

# Final level only
inferred_complexity_df <- inferred_complexity_df %>% filter(level_number == 10)

# Sum code communication
inferred_complexity_df$communication <- factor(inferred_complexity_df$communication)
contrasts(inferred_complexity_df$communication) = contr.sum(2)
contrasts(inferred_complexity_df$communication)

# Dummy code complexity
inferred_complexity_df$dummy_complexity_mid <- 0
inferred_complexity_df$dummy_complexity_mid[inferred_complexity_df$concept_number == 2] <- 1 
inferred_complexity_df$dummy_complexity_mid <- factor(inferred_complexity_df$dummy_complexity_mid)
  
inferred_complexity_df$dummy_complexity_high <- 0
inferred_complexity_df$dummy_complexity_high[inferred_complexity_df$concept_number == 3] <- 1 
inferred_complexity_df$dummy_complexity_high <- factor(inferred_complexity_df$dummy_complexity_high)

xmdl_control = lm(learner_inferred_complexity ~ dummy_complexity_mid + dummy_complexity_high, data=inferred_complexity_df)

xmdl_main <- update(xmdl_control, ~ . + communication)

xmdl_interaction <- update(xmdl_main, ~ . + dummy_complexity_mid:communication + dummy_complexity_high:communication)

summary(xmdl_main)

anova_comp <- anova(xmdl_control, xmdl_main, xmdl_interaction, test='Chisq')
anova_comp

# Generate table for appendix
# xtable(tidy(xmdl_main))
```

# Cumulative Score
# Appendix A, Table S3
# Linear model predicting the learner's final score.
```{r}
final_score_df <- read.csv("~/src/naive_curriculum_exp/ipython/exp1_df.csv")

# Final level only
final_score_df <- final_score_df %>% filter(level_number == 10)

# Sum code communication
final_score_df$communication <- factor(final_score_df$communication)
contrasts(final_score_df$communication) = contr.sum(2)
contrasts(final_score_df$communication)

### Dummy code complexity 
### Set Concept 1 as reference

final_score_df$dummy_complexity_mid <- 0
final_score_df$dummy_complexity_mid[final_score_df$concept_number == 2] <- 1 
final_score_df$dummy_complexity_mid <- factor(final_score_df$dummy_complexity_mid)

final_score_df$dummy_complexity_high <- 0
final_score_df$dummy_complexity_high[final_score_df$concept_number == 3] <- 1 
final_score_df$dummy_complexity_high <- factor(final_score_df$dummy_complexity_high)

summary(final_score_df$dummy_complexity_high)

xmdl_main = lm(cum_player_score ~ communication 
               + dummy_complexity_mid 
               + dummy_complexity_high, 
               data=final_score_df)

xmdl_interaction <- update(xmdl_main, ~ . 
                           + dummy_complexity_mid:communication 
                           + dummy_complexity_high:communication)

summary(xmdl_interaction)
anova_comp <- anova(xmdl_main, xmdl_interaction, test='Chisq')
anova_comp

## Generate table for appendix
#xtable(tidy(xmdl_interaction))
```


# Learning Rate
# Appendix D
# Mixed effects model predicting per-level score
```{r}
complexity_per_level_scores_df <- read.csv("~/src/naive_curriculum_exp/ipython/exp1_df.csv")

# Center boolean_complexity
complexity_per_level_scores_df$boolean_complexity_centered <- complexity_per_level_scores_df$boolean_complexity - (1 + 4 + 6) / 3

# Sum code communication
complexity_per_level_scores_df$communication <- factor(complexity_per_level_scores_df$communication)
contrasts(complexity_per_level_scores_df$communication) = contr.sum(2)
contrasts(complexity_per_level_scores_df$communication)

# Null model uses only task UUID
xmdl_null = lmer(pct_max_score ~ (1|task_uuid), complexity_per_level_scores_df)
xmdl_main <- update(xmdl_null, ~ . + boolean_complexity_centered + communication + level_number)
xmdl_two_way <- update(xmdl_main, ~ . + (boolean_complexity_centered + level_number + communication)^2)
xmdl_three_way <- update(xmdl_two_way, ~ . + boolean_complexity_centered*communication*level_number)

summary(xmdl_three_way)

anova_all_comp <- anova(xmdl_null, xmdl_main, xmdl_two_way, xmdl_three_way, test='Chisq')
anova_all_comp

## Generate table for appendix
# xtable(tidy(xmdl_three_way))
```

##### EXPERIMENT 2 ##### 

# Transmission Fidelity
# Main paper, section 3.2.1
# Biniomial-Logistic regression on number of successes on post-trial questionnaire.
```{r}
logistic_viz_df <- read.csv("~/src/naive_curriculum_exp/ipython/exp2_df.csv") 

# Filter just for final level
logistic_viz_df <- logistic_viz_df %>% filter(level_number == 10)

# Optional: filter out "bad" teachers (Appendix B, Table )
# logistic_viz_df <- logistic_viz_df %>% filter(bad_teacher == 'False')

# Switch complexity to categorical and sum-code it
logistic_viz_df$boolean_complexity[logistic_viz_df$concept_number == 1] <- 'low' 
logistic_viz_df$boolean_complexity[logistic_viz_df$concept_number == 2] <- 'high'
logistic_viz_df$boolean_complexity <- factor(logistic_viz_df$boolean_complexity)
contrasts(logistic_viz_df$boolean_complexity) = contr.sum(2)

# Sum code communication
logistic_viz_df$communication <- factor(logistic_viz_df$communication)
contrasts(logistic_viz_df$communication) = contr.sum(2)

# Sum code context
logistic_viz_df$context <- factor(logistic_viz_df$visibility)
contrasts(logistic_viz_df$context) = contr.sum(2)

logistic_viz_df$successes <- logistic_viz_df$learner_concept * 8
  
xmdl_main <- glm( cbind(successes, 8 - successes) ~ context + communication + boolean_complexity, family='binomial', data=logistic_viz_df)
xmdl_interaction <- update(xmdl_main, ~ . + context:communication)

summary(xmdl_interaction)
xtable(tidy(xmdl_interaction))

anova(xmdl_main, xmdl_interaction, test='Chisq')

# Generate table for appendix
# xtable(tidy(xmdl_interaction))
```

# Cumulative Score
# Main paper, section 3.2.2
# Linear model predicting the learner's final score.
```{r}
context_final_score_df <- read.csv("~/src/naive_curriculum_exp/ipython/exp2_df.csv") 
context_final_score_df <- context_final_score_df %>% filter(level_number == 10)

# Filter out "bad" teachers (Appendix B)
# context_final_score_df <- context_final_score_df %>% filter(bad_teacher == 'False')

# High / low complexity
context_final_score_df$boolean_complexity[context_final_score_df$concept_number == 1] <- 'low' 
context_final_score_df$boolean_complexity[context_final_score_df$concept_number == 2] <- 'high'
context_final_score_df$boolean_complexity <- factor(context_final_score_df$boolean_complexity)
contrasts(context_final_score_df$boolean_complexity) = contr.sum(2)
contrasts(context_final_score_df$boolean_complexity)

# Sum code communication
context_final_score_df$communication <- factor(context_final_score_df$communication)
contrasts(context_final_score_df$communication) = contr.sum(2)
contrasts(context_final_score_df$communication)

# Sum code context
context_final_score_df$context <- factor(context_final_score_df$visibility)
contrasts(context_final_score_df$context) = contr.sum(2)
contrasts(context_final_score_df$context)

summary(context_final_score_df)

xmdl_main <- lm(cum_player_score ~ boolean_complexity + communication  + context, data=context_final_score_df)
xmdl_two_way <- update(xmdl_main, ~ . + communication:context)

summary(xmdl_two_way)

anova_viz_comp <- anova(xmdl_main, xmdl_two_way, test='Chisq')
anova_viz_comp

# Generate table for appendix
# xtable(tidy(xmdl_key_two_way))
```

# Analysis of Optimal Demonstrations
# Main paper, section 3.2.3
# ANOVA testing for number of optimal demonstrations per condition.
```{r}
optimal_demo_df <- read.csv("~/src/naive_curriculum_exp/ipython/exp2_demonstrations_df.csv") 

optimal_demo_df$group <- paste(optimal_demo_df$visibility, optimal_demo_df$boolean_complexity)

summary(optimal_demo_df)
optimal_demo_df$group <- factor(optimal_demo_df$group)
levels(optimal_demo_df$group)

anova <- aov(n_optimal_demonstrations ~ group, data=optimal_demo_df)

summary(anova)
```

# Analysis of Subjective Difficulties
# Main paper, section 3.2.3
# ANOVA testing reported difficulties across conditions and roles.
```{r}
difficulty_survey <- read.csv("~/src/naive_curriculum_exp/ipython/exp2_survey_difficulty_df.csv") 
difficulty_survey$group <- factor(difficulty_survey$group)

intermediate_difficulty <- difficulty_survey %>% filter(concept_number == 2)

nrow(intermediate_difficulty)

anova <- aov(difficulty ~ group, data=intermediate_difficulty)
summary(anova)

multcomps = glht(anova, linfct = mcp(group = "Tukey"))
summary(multcomps)

# xtable(tidy(multcomps))
```

# Learning Rate
# Appendix D
# Mixed effects model predicting per-level score
```{r}
context_mixed_df <- read.csv("~/src/naive_curriculum_exp/ipython/exp2_df.csv") 

# High / low complexity
context_mixed_df$boolean_complexity[context_mixed_df$concept_number == 1] <- 'low' 
context_mixed_df$boolean_complexity[context_mixed_df$concept_number == 2] <- 'high'
context_mixed_df$boolean_complexity <- factor(context_mixed_df$boolean_complexity)
contrasts(context_mixed_df$boolean_complexity) = contr.sum(2)
contrasts(context_mixed_df$boolean_complexity)

# Sum code communication
context_mixed_df$communication <- factor(context_mixed_df$communication)
contrasts(context_mixed_df$communication) = contr.sum(2)
contrasts(context_mixed_df$communication)

# Sum code context
context_mixed_df$context <- factor(context_mixed_df$visibility)
contrasts(context_mixed_df$context) = contr.sum(2)
contrasts(context_mixed_df$context)

summary(context_mixed_df)

xmdl_null = lmer(pct_max_score ~ (1|task_uuid), context_mixed_df)
xmdl_main <- update(xmdl_null, ~ . + boolean_complexity + communication + level_number + context)
xmdl_two_way <- update(xmdl_main, ~ . + (communication + level_number + context)^2)
xmdl_three_way <- update(xmdl_two_way, ~ . + context:communication:level_number)
xmdl_all_three_way <- update(xmdl_three_way, ~ . + (boolean_complexity + communication + level_number + context)^3)
xmdl_four_way <- update(xmdl_all_three_way, ~ . + context*communication*level_number*boolean_complexity)

summary(xmdl_four_way)

# Generate table for appendix
# xtable(tidy(xmdl_three_way))

anova_viz_comp <- anova(xmdl_null, xmdl_main, xmdl_two_way, xmdl_three_way, test='Chisq')
anova_viz_comp
```


# Transmission Fidelity
# Author Response
# Biniomial-Logistic regression on number of successes on post-trial questionnaire.
```{r}
logistic_viz_df <- read.csv("~/src/naive_curriculum_exp/ipython/response_exp_df.csv") 

# Filter just for final level
logistic_viz_df <- logistic_viz_df %>% filter(level_number == 10)

# Sum code context
logistic_viz_df$context <- factor(logistic_viz_df$visibility)
contrasts(logistic_viz_df$context) = contr.sum(2)

logistic_viz_df$successes <- logistic_viz_df$learner_concept * 8
  
xmdl_main <- glm( cbind(successes, 8 - successes) ~ context, family='binomial', data=logistic_viz_df)

summary(xmdl_main)
xtable(tidy(xmdl_main))
```

# Concept Knowledge <--> Learner Score
# Author Response
# Linear regression predicting learner score from concept knowledge
```{r}
concept_knowledge_to_score_df <- read.csv("~/src/naive_curriculum_exp/ipython/exp1_df.csv")

# Final level only
concept_knowledge_to_score_df <- concept_knowledge_to_score_df %>% filter(level_number == 10)

xmdl_main <- lm(cum_player_score ~ learner_concept, data=concept_knowledge_to_score_df)

summary(xmdl_main)

xtable(tidy(xmdl_main))
```

# Demonstration Optimality <--> Teacher Difficulty
# Author Response
# Linear regression(s) predicting teacher reported difficulty from optimality criteria
```{r}
demo_optimality <- read.csv("~/src/naive_curriculum_exp/ipython/demonstration_optimality_and_difficulty.csv")

xmdl_main <- lm(difficulty_teacher ~ optimal_score, data=demo_optimality)

summary(xmdl_main)

xtable(tidy(xmdl_main))
```
```{r}
xmdl_main <- lm(difficulty_teacher ~ optimal_features, data=demo_optimality)

summary(xmdl_main)

xtable(tidy(xmdl_main))
```

# Demonstration Optimality <--> Condition
```{r}
optimal_demo_df <- read.csv("~/src/naive_curriculum_exp/ipython/demonstration_optimality_by_condition.csv") 

optimal_demo_df$group <- paste(optimal_demo_df$visibility, optimal_demo_df$boolean_complexity)

summary(optimal_demo_df)
optimal_demo_df$group <- factor(optimal_demo_df$group)
levels(optimal_demo_df$group)

# By "optimal score"
anova <- aov(optimal_score ~ group, data=optimal_demo_df)
summary(anova)

# By "optimal features"
anova <- aov(optimal_features ~ group, data=optimal_demo_df)
summary(anova)
```
```